%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \experienceentry
  {The Walt Disney Company\entrydatetotalstyle{~~~·~~~2 yrs 11 mos }} % Company
    {Senior Software Engineer - Disney+, Hulu, ESPN+} % Position
    {Chicago, Illinois} % Location
    {June 2022 - Present} % Date(s)
    {Develop and maintain a unified commerce platform serving millions of global users across Disney+, Hulu, and ESPN+. My role focuses on delivering robust, efficient software solutions that ensure a cohesive and intuitive user experience across all three streaming services.}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Collaborated with solution owners and architects to deliver optimal customer solutions.}
      	\item {Led design and development of scalable backend services and APIs.}
		\item {Translated complex business needs into reliable technical solutions.}
		\item {Owned end-to-end feature delivery from architecture to production.}
		\item {Improved system performance by identifying and resolving bottlenecks.}
		\item {Mentored junior engineers and upheld high code standards.}
		\item {Enforced best practices for testing, documentation, and code quality.}
		\item {Worked with DevOps to streamline CI/CD and improve observability.}
		\item {Ensured compliance with security, privacy, and regulatory standards.}
		\item {Contributed to technical roadmaps and long-term architecture planning.}
		\item {Researched and proposed emerging technologies to enhance the platform.}
		\item {Handled backend traffic exceeding 8K requests per second (RPS) with high availability and low latency.}
		\item {Reduced build times by 50\%, significantly accelerating deployment cycles and team productivity.}
		\item {Provided technical leadership within the team, influencing architectural decisions and coding standards.}
		\item {Drove cross-team initiatives to improve engineering practices across the organization.}
		\item {Acted as a go-to expert and mentor, fostering a culture of continuous learning and high performance.}
      \end{cvitems}
    }
    {Java, Spring Boot, Reactor, Weblux, Kubernetes, JUnit, Gradle, Jenkins, Spinnaker, AWS, rest, grpc, GraphQL}

%---------------------------------------------------------
  \experienceentry
  {Slalom\entrydatetotalstyle{~~~·~~~4 yrs 10 mos }} % Company
    {Senior Software Engineer} % Position
    {Chicago, Illinois} % Location
    {July 2017 - June 2022} % Date(s)
    {As a Slalom Build member, I have worked for several customers in different industries: Health Care, Financial and Automotive. Part of my day to day duties are:}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Collaborating with solution owners, architects and other team members to build the best solution for the customer.}
      	\item {Developing new features using the best standards in the industry, to produce a highly maintainable and scalable software.}
      	\item {Verifying and validating features via unit testing, integration testing and end to end testing.}
      	\item {Fixing defects and bugs.}
      	\item {Mentoring and helping junior developers.}
        \item {Participating to all Agile ceremonies.}
      \end{cvitems}
    }
    {Java, Kotlin, Spring Boot, Spring Cloud, Dropwizard, Apache Camel, JUnit, Gradle, Maven, Jenkins, PCF, AWS, Microsoft Azure.}
%--------------------------------------------------------- 
  
  \experienceentryextra
    {Senior Software Engineer} % Job title
    {Software Engineer} % Job title 2
    {Peapod\entrydatetotalstyle{~~~·~~~2 yrs}} % Organization
    {Chicago, Illinois} % Location
    {Jan. 2017 - July 2017} % Date1
    {Sep. 2015 - Jan. 2017} % Date2
    {Member of the Web Center team, in charge of developing and maintaining several public websites. Some of my daily responsibilities include:
    } % Details
    {
    	\begin{cvitems}
  		\item Collaborating with product owners, business analysts and other team members in a cross-functional Agile environment to produce a content management system that is fully integrated with various loyalty, coupon, and user account systems.
  		\item Developing a Spring MVC proxy application around our ESB to allow OAuth2 protected REST APIs to be used by our websites.
  		\item Developing a modular REST-driven integration API using Apache Camel, Karaf, ActiveMQ and various other libraries.
  		\item Designing and implementing new features using TDD (Test Driven Development).
  		\item Verifying and validating features via unit testing, integration testing and automated acceptance testing (Serenity BDD).
  		\item Participating in support rotation and troubleshooting production issues to ensure the continued operations of the business.
  		\item Improving software quality, reusability, extensibility and consistency.
	\end{cvitems} 
    }
    {Java, Spring, Apache Camel, OSGi, OAuth2, ActiveMQ, Karaf.}
    
%---------------------------------------------------------
  
  \experienceentry
  	{Pros\entrydatetotalstyle{~~~·~~~3 yrs 8 mos}} % Company
    {Software Consultant} % Position
    {Chicago, Illinois} % Location
    {Feb. 2012 - Sep. 2015} % Date(s)
    {I was part of the Professional Services team providing expertise to customers related to the
Configure/Price/Quote (CPQ) solutions and more specifically involved in the following activities:}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        	\item Integrating Pros CPQ solutions in the IT landscape by using web services.
			\item Interfacing Pros CPQ solutions for data loading purposes.
			\item Development of additional Java EE plugins to fit specific customer needs.
    		\item Designing the User Interface (HTML based xml files, CSS, Javascript).
    		\item Java-based macrolanguage developing and use of built-in configuration tools.
    		\item Responsible for deploying in our Cloud environment.
    		%\item Issue management/resolution in a SaaS environment.
      \end{cvitems}
    }
    {Java, JavaScript, HTML, CSS, Salesforce.com (Apex, Force.com), Oracle, JBoss, JSON, XML, SOAP.}
%---------------------------------------------------------
  
  \experienceentry
  	{Fujitsu Technology Solutions\entrydatestyle{~~~·~~~5 mos}} % Company
    {Java Developer} % Position
    {Luxembourg City, Luxembourg} % Location
    {Apr. 2011 - Aug. 2011} % Date(s)
    {} % Description
    {
    	\begin{cvitems} % Details
        	\item Made a solution to improve the way to use Arquillian.
			\item Improved the company test process by the creation of a Maven plugin which generates an Arquillian test class.
			\item Using the reflection API, automated search of dependencies needed for the archive deployed on the server.
      	\end{cvitems}
    }
    {Maven, JUnit, EJBs, Cobertura.}

%---------------------------------------------------------
\end{cventries}
