%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{personnal projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \projectentry
    {Android Application} % Project type
    {Chicago Commutes} % Name
    {2014 - Present} % Date(s)
    {Android application that helps commuting in Chicago. CTA (trains/buses) \& Divvy (bikes).\linebreak
\tech{Technology used: Kotlin, JSON, Google Maps APIs, Mapbox, RxJava, Redux, Realm.}
    }
    {
    \begin{projectdetails}
        	\item Source code: \href{https://github.com/carlphilipp/chicago-commutes}{https://github.com/carlphilipp/chicago-commutes}
		\item Download on Play Store: \href{https://play.google.com/store/apps/details?id=fr.cph.chicago}{https://play.google.com/store/apps/details?id=fr.cph.chicago}
		\item Download on F-Droid: \href{https://f-droid.org/en/packages/fr.cph.chicago.foss}{https://f-droid.org/en/packages/fr.cph.chicago.foss}
      \end{projectdetails}
   }

%---------------------------------------------------------
  \vspace{-2.0mm}
  \projectentry
    {website} % Project type
    {Cryptax} % Name
    {2018 - Present} % Date(s)
    {Website that generates a report to help you declaring your gains in Crypto currency trading to the IRS. I mainly worked on the rest APIs.\linebreak
    \tech{Technology used: Kotlin, Google Cloud, Spring Boot, RxJava, Docker.}
    }
    {
    \begin{projectdetails}
        	\item Website: \href{https://www.cryptax.app}{https://www.cryptax.app}
		\item Source code: \href{https://github.com/cryptax-org}{https://github.com/cryptax-org}
      \end{projectdetails}
    }

%---------------------------------------------------------
  \vspace{-2.0mm}
  \projectentry
  	{RESTFUL API} % Project type
  	{Be My Chef} % Name
  	{2014 - 2016} % Date(s)
    {Java-based RESTful API.\linebreak
\tech{Technology used : Java, Maven, Spring Boot, Jackson, JSON, JUnit, Mockito, Stripe, Mandrill, GeoJSON, Quartz, Findbugs, Jacoco, PMD, MongoDB, JIRA, Git.}
    }
    {
    \begin{projectdetails}
        	\item Source code: \href{https://github.com/carlphilipp/be-my-chef}{https://github.com/carlphilipp/be-my-chef}
      \end{projectdetails}
    }
%---------------------------------------------------------

\end{cventries}
\vspace{-2.0mm}
